\documentclass[a4paper,10pt]{article}

\usepackage[a4paper,margin=0.46in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{array}
\usepackage{setspace}

\hypersetup{
colorlinks=true,
urlcolor=blue
}

\pagenumbering{gobble}
\setstretch{0.97}
\setlength{\parindent}{0pt}

% ---------- SECTION STYLE ----------
\titleformat{\section}
{\large\bfseries\uppercase}
{}{0em}{}[\titlerule]


\begin{document}

% ---------- HEADER ----------
\begin{center}

{\Huge \scshape Aditya Sahu} \\[3pt]

Web Developer | MERN Stack Developer \\[5pt]

\small
\href{tel:+917985693955}{\faPhone\ \underline{+91 7985 693 955}}
\hspace{5pt}
\href{mailto:adityasahu.dev@gmail.com}{\faEnvelope\ \underline{adityasahu.dev@gmail.com}}
\hspace{5pt}
\href{https://linkedin.com/in/adityasahu-dev}{\faLinkedin\ \underline{LinkedIn}}
\hspace{5pt}
\href{https://github.com/Codexadi25}{\faGithub\ \underline{GitHub}}

\end{center}

\vspace{-8pt}

% ---------- OVERVIEW ----------
\section*{Overview}

Motivated and self-driven BCA student with practical experience building MERN Stack applications, backend systems, and real-world business solutions. Interested in backend development, automation workflows, scalable APIs, and AI-assisted systems. Built personal and client-focused projects while continuously learning modern development technologies and problem-solving approaches.

\vspace{-3pt}

% ---------- EDUCATION ----------
\section*{Education}

\textbf{Chhatrapati Shahu Ji Maharaj University, Kanpur}
\hfill \textit{Bachelor of Computer Applications (BCA)}

\textbf{Laughing Buddha Academy, Kanpur}
\hfill \textit{Higher Secondary \& Senior Secondary Education}

\vspace{-3pt}

% ---------- PROJECTS ----------
\section*{Projects}

\textbf{RevenueOS — AI Business Optimization Platform (Ongoing)}
\hfill \textit{React.js, Node.js, MongoDB, n8n}

\href{http://revenueos.web.app/}{revenueos.web.app}

\begin{itemize}
    \item Developing a business intelligence platform focused on workflow analysis, automation, and customer experience improvement using AI-driven insights.
    \item Integrating n8n automation pipelines for workflow optimization and operational efficiency.
\end{itemize}

\vspace{-4pt}

\textbf{NEX Log Logistics Management System}
\hfill \textit{React.js, Express.js, MongoDB}

\href{https://nexloglogistics.web.app/}{nexloglogistics.web.app}

\begin{itemize}
    \item Built a logistics and shipment management platform with order handling and operational workflow tracking.
    \item Implemented SVG-to-data conversion for storing multimedia directly inside MongoDB, reducing third-party storage dependency and infrastructure costs.
\end{itemize}

\vspace{-4pt}

\textbf{SupportHub (WIMOBOT)}
\hfill \textit{Node.js, Express.js, MongoDB}

\href{https://wimobot.onrender.com/}{wimobot.onrender.com}

\begin{itemize}
    \item Developed a backend-focused support system with ticket workflows, canned responses, messaging features, and admin management tools.
    \item Designed modular REST APIs and scalable backend architecture for organized support operations.
\end{itemize}

\vspace{-4pt}

\textbf{DhanLaxmi Enterprises — Official Website}
\hfill \textit{React.js, Firebase, Firestore}

\href{https://dhanlaxmien.web.app/}{dhanlaxmien.web.app}

\begin{itemize}
    \item Developed and deployed a responsive business website with Firebase Hosting and Firestore integration for lead management and business branding.
    \item Implemented responsive UI, real-time d\input{Resume_Updated}ata handling, and custom deployment workflow.
\end{itemize}

\vspace{-4pt}

\textbf{Browser Media Player}
\hfill \textit{React.js, JavaScript}

\begin{itemize}
    \item Built a browser-based media player supporting videos, images, and PDFs with playback controls and file navigation features.
\end{itemize}

\vspace{-3pt}

% ---------- SKILLS ----------
\section*{Technical Skills}

\begin{tabular}{@{}p{3.8cm}p{11.5cm}}

\textbf{Languages:} & JavaScript, Python \\

\textbf{Frontend:} & React.js and React Native, HTML5, CSS3, Responsive UI \\

\textbf{Backend:} & Node.js, Express.js, REST APIs \\

\textbf{Databases:} & MongoDB, Firebase Firestore, MySQL (basic), PostgreSQL (basics) \\

\textbf{Tools:} & Git, GitHub, Postman, Firebase, Docker, K8S \\

\textbf{Learning:} & n8n, AI Workflow Automation \\

\end{tabular}

\vspace{-3pt}

% ---------- ADDITIONAL ----------
\section*{Additional Information}

\begin{tabular}{@{}p{2.5cm}p{10cm}}
\textbf{Languages:} & Hindi, English \\
\textbf{DOB:} & 25 October 2004 \\
\end{tabular}

\end{document}
